\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Jaison Dennis} % Your name
% You can merge both of these into a single line, if you do not have a website.
\address{+91 91885 00270 \\ Kochi, Kerala} 
\address{\href{mailto:jaisondennis.mec@gmail.com}{jaisondennis.mec@gmail.com} \\ \href{https://linkedin.com/in/jaison080}{linkedin.com/in/jaison080} \\
	\href{https://github.com/jaison080}{github.com/jaison080} \\ \href{jaisondennis.netlify.app}{jaisondennis.netlify.app}}  %

\begin{document}
	
	%----------------------------------------------------------------------------------------
	%	OBJECTIVE
	%----------------------------------------------------------------------------------------
	
	\begin{rSection}{About Me}
		
		{
			
			\centering{\textbf{“BETTER 3 HOURS TOO SOON THAN A MINUTE TOO LATE”}}\\
			A passionate Full-Stack Developer and an enthusiastic learner awaiting chances to explore, currently a CS undergrad at Model Engineering College Thrikkakkara. }
		
		
	\end{rSection}
	%----------------------------------------------------------------------------------------
	%	EDUCATION SECTION
	%----------------------------------------------------------------------------------------
	
	\begin{rSection}{Education}
		
		{\bf{B.Tech in Computer Science} , Model Engineering College (CGPA : 9.1) \hfill {Expected 2024}\\
		
		{\bf Class 12}, CBSE (95.4\%)\hfill {2020}}\\
	\\{\bf Class 10, ICSE (91.6\%)\hfill {2018}}
		%Minor in Linguistics \smallskip \\
		%Member of Eta Kappa Nu \\
		%Member of Upsilon Pi Epsilon \\
		
		
	\end{rSection}
	
	%----------------------------------------------------------------------------------------
	% TECHINICAL STRENGTHS	
	%----------------------------------------------------------------------------------------
	\begin{rSection}{SKILLS}
		
		\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
			Frontend Technologies & React js, Next js, HTML, CSS, Hugo, Flutter, Dart
			\\
			Backend Technologies & Node js, Firebase, Supabase\\
			Programming Languages & C, C++, Java, Python, Rust\\
				Databases and Cloud Hosting & Mongo DB, Firebase, Supabase, Netlify, Vercel, Cloudflare, Docker\\
		\end{tabular}\\
	\end{rSection}
	
	\begin{rSection}{EXPERIENCE}
		
			\textbf{Chief Operating Officer} \hfill Jan 2022 - Present\\
			Emerald Rainbow \hfill \textit{Remote}
		\begin{itemize}
			\itemsep -3pt {} 
			\item Manage and co-ordinate with all the team members for the daily work updates.
			\item Organize Review Meetings.
			\item \textbf{Tech Stacks} : HTML,CSS,Next js,Firebase 
		\end{itemize}
		
		\textbf{Junior Web Developer} \hfill May 2022 - Aug 2022\\
		Anile Media \hfill \textit{Maharashtra, Mumbai}
		\begin{itemize}
			\itemsep -3pt {} 
			\item Built company's Main Website.
			\item Maintained Client's websites.
			\item \textbf{Tech Stacks} : HTML,CSS,Next js,Wordpress,Firebase 
		\end{itemize}
	
		
		\textbf{IEDC MEC Collab Tech Lead} \hfill Oct 2022 - Jan 2022\\
	IEDC MEC \hfill \textit{Remote}
	\begin{itemize}
		\itemsep -3pt {} 
		\item Built Collab Platform for IEDC MEC.
		\item A project showcasing platform exclusive for MECians.
		\item \textbf{Tech Stacks} : React js,CSS,Firebase,AWS Serverless Functions 
	\end{itemize}
		
	\end{rSection} 
	
	%----------------------------------------------------------------------------------------
	%	WORK EXPERIENCE SECTION
	%----------------------------------------------------------------------------------------
	
	\begin{rSection}{PROJECTS}
		\vspace{-1.25em}
		\item \textbf{Keralolsavam Management Platform.} {Built a website to manage the Keralolsavam (cultural and sports competitions of Kerala in which students participate from all districts) Pre-Events of Ernakulam District.The project had features like live news,event participant listing,assigning of chest no's to participants,live scoreboard and also results.It had an admin and a official dashboard.Admin has the right to add news and assign officials different events.The officials has the right to update score for each participant and also assign chest no's too.The officials can also update news.The winners are calculated automatically based on the marks and there are much more features too.. \href{https://keralolsavam.vercel.app/}{(Try it here)}}
		\item \textbf{IEDC MEC Collab.} {Collab MEC envisions creating world class developers and world class projects and a wide network of developers.Collab MEC sets its sights on enhancing the coding culture in MEC and in turn the quality of projects and developers made in MEC. With Collab, every developer finds a project and every project finds its developers.\href{https://collab.iedcmec.in/}{(Try it here)}}
		\item \textbf{Blind Guru.} {Developing A Web-App for blind people for helping them read SMS , Whatsapp
			Messages,Facebook Captions,Twitter Feeds,etc...This project got one of the top prizes for Beach Hack 4.\href{https://blind-guru.netlify.app/}{(Try it here)}}
			\item \textbf{Simplify Chat 2.0.} {A fully functional MERN Chatting App with features like group chats and realtime notifications too.\href{https://simplify-chat.herokuapp.com/}{(Try it here)}}
			\item \textbf{Rainbow} {A fnon toxic social media platform.\href{https://rainbow-emerald.netlify.app/}{(Try it here)}}
	\end{rSection} 
	
	%----------------------------------------------------------------------------------------
	\begin{rSection}{Volunteering} 
		\begin{itemize}
			\item 	\textbf{ Web Lead - DSC MEC.}
				\item 	\textbf{ CS Tech Team - Excel MEC.}
			\item 	\textbf{ Web Team - Excel MEC.}
			\item 	\textbf{ App Team - Excel MEC.}
			
					\item 	\textbf{ Tech Sub Head - TLE MEC.}
						\item 	\textbf{ Tech Team - IEDC MEC.}
							\item 	\textbf{ Tech Team - FOSS MEC.}
								\item 	\textbf{ Joint Secretary - IETE SF MEC.}
								\item 	\textbf{ Media Sub Head - Tinkerhub MEC.}
								
		\end{itemize}
		
		
	\end{rSection}
	
	
	
\end{document}
